### 2018-01-31 includes/stringfuzz.tex
Reverting some changes addressed in review. Made tables look scientific. Made sure tables were no longer than line width. Added footnotes rather than column for Ifaz transformations.

\fuzzer{} is implemented as a Python package, and comes with several
executables to generate, transform, and analyze \smtfull{} string and regex
instances. Its components are implemented as \unix{} ``filters'' to enable easy
integration with other tools (including themselves). For example, the
outputs of generators can be piped into transformers, and transformers
can be chained to produce a stream of tuned inputs to a
solver. \fuzzer{} is composed of the following tools:

\begin{description}
    \item[\generator{}] \hfill \\
    This tool generates \smt{} instances. It supports several generators and
    options that specify its output. Details can be found in
    Table~\ref{tbl:generators}.
    \item[\transformer{}] \hfill \\
    This tool transforms \smt{}
    instances. It supports several transformers and options that specify
    its output and input, which are explained in
    Table~\ref{tbl:transformers}. Note that transformers
    \textit{Translate} and \textit{Reverse} also preserve
    satisfiability under certain conditions~\cite{ifaz}.
    \item[\texttt{stringstats}] \hfill \\
    This tool takes an \smt{}
    instance as input and outputs its properties: the number of
    variables/literals, the max/median syntactic depth of expressions, the
    max/median literal length, etc.
\end{description}

We organized \fuzzer{} to be easily extended. As evidence of our success we note
that while the whole project 
contains \linesInFuzzer{} lines of code, it takes an average of 
\linesPerX{} lines of code to create a transformer. \fuzzer{} can either be 
installed from source, or from the Python PIP package
repository.\footnote{The link to the source code will be added after double-blind review.}

\begin{table}[t]
    \centering
    \caption{\generator{} built-in generators.}
    \label{tbl:generators}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}
        & \textbf{Generate instances that have ...}
        \\ \hline
        \textit{Concats}
        & Long concats and optional random extracts.
        \\ \hline
        \textit{Lengths}
        & Many variables (and their concats) with length constraints.
        \\ \hline
        \textit{Overlaps}
        & An expression of the form A.X = X.B.
        \\ \hline
        \textit{Equality}
        & An equality among concats, each with variables or constants.
        \\ \hline
        \textit{Regex}
        & Regexes of varying complexity.
        \\ \hline
        \textit{Random-Text}
        & Random, likely syntactically \textit{in}valid text.
        \\ \hline
        \textit{Random-AST}
        & Random, but semantically \textit{valid} text.
        \\ \hline
    \end{tabular}

    \caption{\transformer{} built-in transformers.}
    \label{tbl:transformers}
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Name}
        & \textbf{The transformer ...}
        & \textbf{Guarantee}\footnote{See Appendix for proofs and restrictions.}
        \\ \hline
        \textit{Fuzz}
        & Randomly replaces literals and operators with similar ones.
        & Well-formed
        \\ \hline
        \textit{Graft}
        & For each sort, swaps a random non-leaf node with a leaf node.
        & Well-formed
        \\ \hline
        \textit{Multiply}
        & Multiplies each number by N, and repeats each character N times.
        & Sat-sat
        \\ \hline
        \textit{Nop}
        & Does not transform (can translate between \smtfull{}).
        & Equisat
        \\ \hline
        \textit{Reverse}
        & Reverses all string literals and concat arguments.
        & Equisat
        \\ \hline
        \textit{Rotate}
        & Performs a syntax tree rotation on compatible operators.
        & Well-formed
        \\ \hline
        \textit{Translate}
        & Permutes the alphabet.
        & Equisat
        \\ \hline
        \textit{Unprintable}
        & Randomly replaces all characters in literals with unprintable ones.
        & Equisat
        \\ \hline
    \end{tabular}
\end{table}

\subsubsection{Regex Fuzzing Capabilities}

\fuzzer{} can generate
and transform instances with regular expression constraints. For example, the
command \texttt{stringfuzzg regex} invokes the regex instance
generator and produces an instance of the form:
\begin{align*}
    & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
    & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
    & \texttt{(assert (<= Min (str.len X)))}? \\
    & \texttt{(assert (<= (str.len X)) Max)}?
\end{align*}

@@

\fuzzer{} can also transform problem instances.
This is done by manipulating parsed syntax trees.
By default most of the built-in transformers 
only guarantee well-formedness, however,
some can even guarantee equisatisfiability. Table~\ref{tbl:transformers} 
lists the built-in transformers and these guarantees.

>>>>

\fuzzer{} is implemented as a Python package, and comes with several
executables to generate, transform, and analyze \smtfull{} string and regex
instances. Its components are implemented as \unix{} ``filters'' to enable easy
integration with other tools (including themselves). For example, the
outputs of generators can be piped into transformers, and transformers
can be chained to produce a stream of tuned inputs to a
solver. \fuzzer{} is composed of the following tools:
\begin{description}
    \item[\generator{}] \hfill \\
    This tool generates \smt{} instances. It supports several generators and
    options that specify its output. Details can be found in
    Table~\ref{tbl:generators}.
    \item[\transformer{}] \hfill \\
    This tool transforms \smt{}
    instances. It supports several transformers and options that specify
    its output and input, which are explained in
    Table~\ref{tbl:transformers}. Note that transformers
    \textit{Translate} and \textit{Reverse} also preserve
    satisfiability under certain conditions~\cite{ifaz}.
    \item[\texttt{stringstats}] \hfill \\
    This tool takes an \smt{}
    instance as input and outputs its properties: the number of
    variables/literals, the max/median syntactic depth of expressions, the
    max/median literal length, etc.
\end{description}
We organized \fuzzer{} to be easily extended. As evidence of our success we note
that while the whole project 
contains \linesInFuzzer{} lines of code, it takes an average of 
\linesPerX{} lines of code to create a transformer. \fuzzer{} can either be 
installed from source, or from the Python PIP package
repository.\footnote{The link to the source code will be added after double-blind review.}

\begin{table}[t]
    \caption{\fuzzer{} built-in (a) generators and (b) transformers.}
    \begin{subtable}{1\textwidth}
        \centering
        \caption{\generator{} built-in generators.}
        \label{tbl:generators}
        \begin{tabular}{ l l }
            \toprule
            \textbf{Name}
            & \textbf{Generates instances that have ...} \\
            \midrule
            \textit{Concats}
            & Long concats and optional random extracts. \\
            \textit{Lengths}
            & Many variables (and their concats) with length constraints. \\
            \textit{Overlaps}
            & An expression of the form A.X = X.B. \\
            \textit{Equality}
            & An equality among concats, each with variables or constants. \\
            \textit{Regex}
            & Regexes of varying complexity. \\
            \textit{Random-Text}
            & Random, likely syntactically \textit{in}valid text. \\
            \textit{Random-AST}
            & Random, but semantically \textit{valid} text. \\
            \bottomrule
        \end{tabular}
    \end{subtable}
    \begin{subtable}{1\textwidth}
        \centering
        \caption{\transformer{} built-in transformers.}
        \label{tbl:transformers}
        \begin{tabular}{l l}
            \toprule
            \textbf{Name}
            & \textbf{The transformer ...} \\
            \midrule
            \textit{Fuzz}
            & Replaces literals and operators with similar ones.\\
            \textit{Graft}
            & Randomly swaps non-leaf nodes with leaf nodes.\\
            \textit{Multiply}\footnote{Satisfiable inputs 
            will produce satisfiable outputs (see Appendix).}
            & Multiplies integers and repeats strings by N.\\
            \textit{Nop}
            & Does nothing (can translate between \smtfull{}).\\
            \textit{Reverse}\footnote{Input and output 
            instances will be equisatisfiable (see Appendix).}
            & Reverses all string literals and concat arguments.\\
            \textit{Rotate}
            & Rotates compatible nodes in syntax tree.\\
            \textit{Translate}\footnotemark[4]
            & Permutes the alphabet.\\
            \textit{Unprintable}
            & Replaces characters in literals with unprintable ones.\\
            \bottomrule
        \end{tabular}
    \end{subtable}
\end{table}

\subsubsection{Regex Fuzzing Capabilities}
\fuzzer{} can generate
and transform instances with regular expression constraints. For example, the
command \texttt{stringfuzzg regex} invokes the regex instance
generator and produces an instance of the form:
\begin{align*}
    & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
    & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
    & \texttt{(assert (<= Min (str.len X)))}? \\
    & \texttt{(assert (<= (str.len X)) Max)}?
\end{align*}

@@

\fuzzer{} can also transform problem instances.
This is done by manipulating parsed syntax trees.
By default most of the built-in transformers 
only guarantee well-formedness, however,
some can even guarantee equisatisfiability. Table~\ref{tbl:transformers} 
lists the built-in transformers and notes these guarantees.

### 2018-01-31 includes/suites.tex
Reverting some changes addressed in review. Made tables look scientific. Made sure tables were no longer than line width. Added footnotes rather than column for Ifaz transformations.

\begin{table}[t]
    \centering
    \caption{\generator{}-generated instances.}
    \label{tbl:generated}
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Name}
            & \textbf{Instances have ...}
            & \textbf{Quantity}
            \\ \hline
        \textit{Concats}
            & A right-heavy, deep tree of concats.
            & 600
            \\ \hline
        \textit{Concats-Balanced}
            & A balanced, deep tree of concats.
            & 100
            \\ \hline
        \textit{Concats-Extracts}
            & A single concat tree, and random character extractions.
            & 600
            \\ \hline
        \textit{Lengths}
            & A single, large length constraint on a variable.
            & 1,000
            \\ \hline
        \textit{Lengths-Concats}
            & Variables and their concats, each with fixed lengths.
            & 500
            \\ \hline
        \textit{Overlaps}
            & A formula of the form A.X = X.B.
            & 100
            \\ \hline
        \textit{Regex}
            & A test for regex membership of arbitrary complexity.
            & 1,200
            \\ \hline
        \textit{Many-Regexes}
            & A test for membership in many random regexes.
            & 600
            \\ \hline
        \textit{Regex-Deep}
            & A test for membership in a regex with many nested operators.
            & 450
            \\ \hline
        \textit{Regex-Pair}
            & A test for membership in one regex, but not another.
            & 600
            \\ \hline
        \textit{Regex-Lengths}
            & A test for membership in a regex, and a length constraint.
            & 600
            \\ \hline
        \textit{Different-Prefix}
            & An equality between two deep concats with different prefixes.
            & 300
            \\ \hline
    \end{tabular}
\end{table}

\begin{table}[t]
    \centering
    \caption{Transformed instances generated by \transformer{}.}
    \label{tbl:transformed}
    \begin{tabular}{|l|l|r|}
        \hline
        \textbf{Name}      & \textbf{Seed}                              & \textbf{Quantity} \\ \hline
        \textit{Amazon}    & Two industrial regex membership instances. & 472 \\ \hline
        \textit{Regex}     & Z3str2 regular expression test suite.      & 7,551 \\ \hline
        \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples.      & 1,170 \\ \hline
    \end{tabular}
\end{table}

>>>>

\begin{table}[t]
    \caption{Repository of \smtfull{} instances}
    \begin{subtable}{1\textwidth}
        \centering
        \caption{\generator{}-generated instances.}
        \label{tbl:generated}
        \begin{tabular}{llr}
            \toprule
            \textbf{Name}
                & \textbf{Instances have a ...}
                & \textbf{Quantity}
            \\
            \midrule 
            \textit{Concats}
                & Right-heavy, deep tree of concats.
                & 600 \\
            \textit{Concats-Balanced}
                & Balanced, deep tree of concats.
                & 100 \\
            \textit{Concats-Extracts}
                & Single concat tree, with character extractions.
                & 600 \\
            \textit{Lengths}
                & Single, large length constraint on a variable.
                & 1,000 \\
            \textit{Lengths-Concats}
                & Tree of fixed-length concats of variables.
                & 500 \\
            \textit{Overlaps}
                & Formula of the form A.X = X.B.
                & 100 \\
            \textit{Regex}
                & Complex regex membership test.
                & 1,200 \\
            \textit{Many-Regexes}
                & Multiple random regex membership tests.
                & 600 \\
            \textit{Regex-Deep}
                & Regex membership test with many nested operators.
                & 450 \\
            \textit{Regex-Pair}
                & Test for membership in one regex, but not another.
                & 600 \\
            \textit{Regex-Lengths}
                & Regex membership test, and a length constraint.
                & 600 \\
            \textit{Different-Prefix}
                & Equality of two deep concats with different prefixes.
                & 300 \\
            \bottomrule
        \end{tabular}
    \end{subtable}

    \begin{subtable}{1\textwidth}
        \centering
        \caption{Transformed instances generated by \transformer{}.}
        \label{tbl:transformed}
        \begin{tabular}{llr}
            \toprule
            \textbf{Name}      & \textbf{Seed}                              & \textbf{Quantity} \\
            \midrule
            \textit{Amazon}    & Two industrial regex membership instances. & 472 \\
            \textit{Regex}     & Z3str2 regular expression test suite.      & 7,551 \\
            \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples.      & 1,170 \\
            \bottomrule
        \end{tabular}
    \end{subtable}
\end{table}
